\section{Exhaustive frontier construction}
\label{sec:frontier}

The phase tables store an exact lowering distance and one deterministic
lowering move for every reachable coordinate.  A maximal record additionally
contains a physical $108$-byte Megaminx state, a verified optimal lowering
word, and masks of all possible first and last moves on optimal paths.  The
table builder derives the maximal layers from the generated distances; the
published counts are comparison controls and are not used to manufacture or
truncate those layers.

For each pair, the first maximal record is combined with the second maximal
record using the lifting rule of \cref{lem:maximal-lifting}.  The checker then
verifies, for every raw pair, that
\begin{enumerate}
  \item its first coordinate is the requested phase-$i$ antipode;
  \item the stored optimal phase-$i$ word reaches the exact chosen
    phase-$(i+1)$ representative;
  \item that intermediate state has the requested second coordinate; and
  \item the stored second-phase word reaches the next subgroup.
\end{enumerate}
Coordinate integers are never treated as physical states.  The raw order is
first-layer major and second-layer minor, and an explicit raw-to-unique map is
constructed without assuming injectivity.  In the regenerated data all
$536{,}572$ and $407{,}628$ physical states are distinct.

\subsection{Exact preprocessing}
\label{sec:exact-preprocessing}

Before neural search, the concatenation of the two optimal lowering words is
processed by exact local transformations.  Consecutive moves on one face are
combined in the face-turn metric; commuting and cancellable moves are
normalized; and meet-in-the-middle dictionaries test windows straddling the
phase boundary.  Every hash match is confirmed by comparing the complete
physical state, and every resulting word is replayed from the corresponding
frontier state.

The published reductions search through $4+4$ boundary windows.  Both runs
use the first seven faces, namely the $28$ FTM moves in $\Sigma_5$; pair 5+6
may therefore leave its source subgroup $G_7$ during preprocessing.  They
close $203$ and $8{,}461$ states respectively.  An
exhaustive symmetry analysis separately reconstructs all $60$
orientation-preserving rotations and retains only maps preserving all nested
subgroups of the pair.  In both cases the admissible stabilizer is the
identity.  Inversion is also rejected: it exchanges the left- and right-coset
conventions, and the exhaustive frontier is not closed under it.  Consequently
no nontrivial orbit reduction is hidden in the coverage counts.

The remaining obligations are therefore the exact ordered ID sets shown in
\cref{tab:coverage-partition}.  The equality in each row is a checked
partition, not a statistical coverage estimate.

\begin{table}[t]
\centering
\caption{Exhaustive partition of the simultaneous-maximal frontiers.}
\label{tab:coverage-partition}
\begin{tabular}{@{}lrrr@{}}
\toprule
Pair & Raw frontier & Exact rewrites & Direct words\\
\midrule
3+4 & 536,572 & 203 & 536,369\\
5+6 & 407,628 & 8,461 & 399,167\\
\midrule
Total & 944,200 & 8,664 & 935,536\\
\bottomrule
\end{tabular}
\end{table}
