\section{Introduction}
\label{sec:introduction}

The Megaminx is a face-turning permutation puzzle with $12$ pentagonal faces,
$20$ movable corners, and $30$ movable edges.  Its state space is too large for
a direct breadth-first computation of the maximum solution length.  As in the
largest certified computations for the Rubik's Cube, useful upper bounds are
therefore obtained by decomposing the solve along a subgroup chain and
certifying the worst-case cost of each transition
\cite{korf1997,kunkle2007,rokicki2013}.

The phase chain studied here was developed in the public Megaminx solver of
Botz~\cite{botz2026dataset}.  In the face-turn metric, its separately computed
phase bounds include the consecutive pairs
\[
  14+8=22
  \qquad\text{and}\qquad
  13+13=26.
\]
The complete externally reported chain has length $114$.  This paper does not
reconstruct the computations outside the two phase pairs considered below;
consequences for that global value are therefore stated conditionally.

Our starting point is a simple boundary-layer observation.  To lower a sum $a+b$
of two integer-valued phase bounds to $a+b-1$, every state for which at least
one constituent phase has distance below its maximum is already harmless.
Only states whose two coordinates are simultaneously maximal require new
solutions.  For phases 3 and 4 this boundary consists of physical lifts of the
Cartesian product
of $212$ and $2{,}531$ coordinates; for phases 5 and 6 it is a product of
$3{,}484$ and $117$ coordinates.  Thus two combined quotients containing
roughly $1.42\times10^{13}$ and $1.66\times10^{15}$ coordinates reduce to
$536{,}572$ and $407{,}628$ explicit proof obligations.

Closing nearly one million individually specified obligations remains a
substantial search problem.  We train compact neural models directly on the
two combined quotients using sparse supervision from random trajectories.
The models rank actions inside one beam per root, evaluated in batches across
many roots on a GPU.  A staged schedule applies narrow beams to the
full unresolved set and reserves wider beams for the diminishing survivor
tail.  Exact local rewriting closes $8{,}664$ states, and the neural-guided
search produces bounded words for the remaining $935{,}536$ in approximately
$6.25$ active A100 GPU-hours.  This aggregate excludes model training, phase
tables, exact rewriting, process gaps, and final replay.

The neural computation is deliberately outside the trusted proof base.  A
checkpoint need not estimate a true distance, and an individual beam search
need not be complete.  The proof uses only the resulting words: the checker
requires an exact partition of the exhaustive frontier, binds every record to
its physical state, enforces the pair-specific length limit, and replays every
direct word without loading a model.  This yields the certified ambient-FTM
upper bounds
\[
  \Gpair{5}{7}\le21,
  \qquad
  \Gpair{7}{9}\le25.
\]

The contributions are therefore:
\begin{enumerate}
  \item a general boundary-layer reduction for improving two consecutive
    subgroup phases by one move;
  \item complete physical constructions of the two simultaneous-maximal
    frontiers, including exact lifting and coordinate round trips;
  \item a proof-oriented neural beam cascade that generates independently
    checkable words for a fixed exhaustive worst-case frontier rather
    than a sampled test distribution; and
  \item deterministic certificate checks establishing the two local
    bounds and, conditional on the reported surrounding phase chain, the
    global reductions $114\to112$ and $114\to111$ when combined with the
    separate color-neutral first-phase result.
\end{enumerate}

We do not claim a new generic beam-search algorithm, exact combined distances,
or ordinary graph diameters.  In particular, combined paths are allowed to
leave their source subgroups under the full FTM move alphabet.  The
mathematical result is exhaustive coverage by bounded words; the learned
search is an effective way of discovering those words.

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  node distance=5.5mm and 8mm,
  box/.style={draw,rounded corners,align=center,minimum height=8mm,
              text width=31mm,font=\small},
  checked/.style={box,fill=blue!6},
  proposer/.style={box,fill=orange!10,draw=orange!70!black},
  arrow/.style={-{Latex[length=2mm]},thick}
]
  \node[checked] (tables) {phase tables\\and maximal layers};
  \node[checked,below=of tables] (frontier) {physical double-max\\frontier};
  \node[proposer,below left=of frontier] (rewrite) {local-rewrite\\generator};
  \node[proposer,below right=of frontier] (neural) {neural-guided\\beam cascade};
  \node[checked,below=27mm of frontier] (certs) {bounded word\\certificates};
  \node[checked,below=of certs] (replay) {coverage checks\\and physical replay};
  \node[checked,below=of replay] (bounds) {certified pair\\upper bounds};
  \draw[arrow] (tables)--(frontier);
  \draw[arrow] (frontier)--(rewrite);
  \draw[arrow] (frontier)--(neural);
  \draw[arrow] (rewrite)--(certs);
  \draw[arrow] (neural)--(certs);
  \draw[arrow] (certs)--(replay);
  \draw[arrow] (replay)--(bounds);
  \node[draw=orange!70!black,dashed,rounded corners,fit=(rewrite)(neural),
        inner sep=2mm,
        label={[font=\footnotesize,text=orange!70!black]right:untrusted proposal}] {};
\end{tikzpicture}
\caption{Proof pipeline and trust boundary.  Both search procedures propose
words; neither procedure is trusted.  The proof consumes only the exhaustive
frontier, the stored words, and the results of deterministic coverage and
replay checks.}
\label{fig:proof-pipeline}
\end{figure}
