\section{Certificate verification and trusted base}
\label{sec:verification}

The search computation answers an existential question for each frontier
state: it proposes a word that appears to reach the target subgroup within the
required limit.  Certification turns those proposals into a finite,
fail-closed proof.  In particular, neither a neural score nor a claim that a
beam exhausted its search space is accepted as evidence.

\subsection{Certificate records and exact coverage}

For each pair, the direct certificates are stored in a SQLite database.  A
row contains the raw state ID, a SHA-256 digest of its 108-byte physical state,
the byte-coded move word and its length, and discovery provenance consisting
of the beam width and checkpoint digest.  A second digest binds the ID, state,
word, and provenance fields.  Database metadata binds the complete collection
to the metric, target subgroup, proof length limit, combined-quotient
definition, physical composition file, and ordered list of unresolved IDs.

Let $I$ be the full raw frontier ID set, $E\subset I$ the IDs closed by exact
rewriting, and $N\subset I$ the IDs represented in the direct-certificate
database.  The checker constructs $I$ and $E$ from regenerated artifacts and
requires
\begin{equation}
  E\cap N=\varnothing,
  \qquad E\cup N=I.
  \label{eq:exact-partition}
\end{equation}
It rejects missing IDs, extra IDs, duplicates, malformed words, stale state
digests, metadata disagreement, and any word longer than the pair-specific
limit.  Thus a partial or interrupted search database cannot be mistaken for
a complete proof.

\subsection{Replay paths and the full-reproduction cross-check}

The proof checker replays every accepted direct word along the first two paths
below.  The full-reproduction entry points additionally require the third:
\begin{enumerate}
  \item the exact 120-position coloring of the combined quotient;
  \item an independently written Python implementation of the full edge and
    corner permutations and orientations; and
  \item a persistent Go verifier compiled against the pinned physical move
    definitions, receiving only the full-state bytes and canonical move word.
\end{enumerate}
The quotient replay establishes arrival at the intended combined target, and
the Python full-state replay applies the physical moves and tests membership in
$G_7$ or $G_9$.  In a full reproduction, the Go path repeats the physical
replay without parsing SQLite or importing the Python transition code.  Python
and Go then independently hash the canonical stream of ID, state bytes, and
word; the workflow requires equality of the SHA-256 transcript digest, first
and last IDs, record count, and maximum length.  Thus aggregate agreement
cannot hide a substituted or omitted record.  Exact-rewrite witnesses are
likewise replayed before their IDs enter $E$.

The committed historical reference reports record the complete Python replay
but predate the transcript-bound Go path and contain no Go transcript fields.
Accordingly, they are not evidence that this newer cross-check was executed for
the published snapshot; rather, the repository makes that cross-check a
fail-closed requirement of a fresh full reproduction.  The mathematical upper
bounds rely on exact coverage and deterministic word replay, while the Go path
is an additional implementation-diversity check on the physical action.

These checks address different failure modes.  Agreement between two
representations cannot by itself prove that the frontier is complete, while an
exact ID partition cannot show that a stored word has the advertised action.
The proof requires both \cref{eq:exact-partition} and successful replay.

\begin{table}[t]
\centering
\caption{Verification roles and their independence boundary.}
\label{tab:verification-roles}
\small
\renewcommand{\arraystretch}{1.12}
\begin{tabularx}{\textwidth}{@{}
  >{\raggedright\arraybackslash}p{0.22\textwidth}
  >{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}X@{}}
\toprule
Component & Implementation & Property checked\\
\midrule
Frontier and partition & deterministic Python pipeline & complete
maximal-layer product and exact ID partition\\
Combined replay & pair-specific Python coloring & every direct word reaches
the intended combined target coordinate\\
Physical replay & Python \texttt{FullStateV1} & every direct word reaches the
physical target subgroup\\
Physical cross-check & persistent Go verifier & separately implemented replay
of the exact same transcript; it shares the pinned move convention\\
Exact rewrites & generated in Go, checked in Python & every accepted rewrite
word has the allowed alphabet and length and physically solves its state\\
\bottomrule
\end{tabularx}
\end{table}

The deterministic coverage checker is not presented as an independent second
implementation of the entire proof.  Independence here is narrower: the two
physical replay engines use separate code paths, and the transcript binding
ensures that they receive the same direct certificates.

\subsection{Regeneration checks}

The full workflow begins before certificate replay.  It downloads a pinned
upstream source archive after verifying its digest, builds the table generator
and verifiers, and regenerates the four complete phase tables.  For every
phase, the checker validates the reachable count, histogram, maximal distance,
maximal-layer count, predecessor structure, and all stored checksums.  It then
reconstructs every maximal physical representative and optimal lowering word,
forms the complete products from \cref{eq:pair34-frontier-size,eq:pair56-frontier-size},
checks the lifting identities of \cref{lem:maximal-lifting}, and regenerates
the exact-rewrite partition.

The published numerical controls are used only for comparison after
generation.  They are not loop bounds for truncating a table or manufacturing
a maximal layer.  Temporary outputs are written under distinct paths, and
payloads with missing records or inconsistent hashes cause the run to stop.

\subsection{Trusted and untrusted components}

The trusted computational base consists of the pinned move and coordinate
definitions, table construction, physical lifting, strict word parsers,
coverage logic, cryptographic hashes as integrity guards, and the replay
implementations.  The neural training code, checkpoints, floating-point
scores, batching order, beam widths, certificate timestamps, and GPU libraries
are outside that base.  The deterministic local-rewrite search is likewise a
word proposer: only its checked outputs enter the proof.  These components can
affect which word is found and how quickly, but cannot make an invalid or
absent word pass the checker.  This separation is the main reason learned
search is suitable here despite lacking completeness or admissibility
guarantees.
