\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage[a4paper,margin=28mm]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,array,tabularx,longtable}
\usepackage{enumitem}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,fit,positioning}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage[nameinlink,capitalise,noabbrev]{cleveref}
\usepackage{listings}
\usepackage{url}
\input{author.tex}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!55!black,
  citecolor=blue!55!black,
  urlcolor=blue!55!black,
  pdftitle={Exhaustive Boundary-Layer Certification for Megaminx via Neural-Guided Beam Cascades},
  pdfauthor={\PaperAuthor}
}
\setlist{nosep}
\lstset{basicstyle=\ttfamily\small,breaklines=true,columns=fullflexible}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\FTM}{\mathrm{FTM}}
\newcommand{\Rsolve}{\mathcal{R}}
\newcommand{\Gpair}[2]{\Rsolve_{\Omega}(G_{#1},G_{#2})}

\title{Exhaustive Boundary-Layer Certification for Megaminx\\
  via Neural-Guided Beam Cascades}
\author{\PaperAuthor\\\small \PaperAffiliation}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
We certify one-move reductions for two adjacent phase pairs in a subgroup-chain
Megaminx solver under the face-turn metric.  The separate worst-case solving
distances of phases 3 and 4 are 14 and 8, while those of phases 5 and 6 are 13
and 13.  A boundary-layer argument shows that improving either sum by one
requires checking only compositions for which both constituent coordinates
are maximally distant from their target subgroups.  This reduces combined
quotients of sizes $14{,}234{,}011{,}545{,}600$ and
$1{,}664{,}617{,}163{,}489{,}280$ to exhaustive frontiers of $536{,}572$ and
$407{,}628$ physical states.  Exact local rewrites certify $8{,}664$ states.
For the remaining $935{,}536$, compact neural action-ranking models guide
batched beam-search cascades that produce bounded solution words.  The models
and search scores are not proof objects.  A deterministic checker requires
exact frontier coverage, while separately implemented replay engines validate
every word proposed by neural-guided search; exact-rewrite words are also
replayed physically.  In the published run the models supplied $935{,}536$
direct certificates in approximately $6.25$ active A100 GPU-hours, excluding
training, preprocessing, and verification.  We thereby obtain the ambient-FTM
bounds
\[
  \Gpair{5}{7}\le 21,
  \qquad
  \Gpair{7}{9}\le 25.
\]
Relative to the externally reported 114-move phase chain, these local results
give the conditional bound 112; together with the separately certified
color-neutral first-phase result, they give the likewise conditional bound
111.  The paper is accompanied by the complete certificate databases, pinned
phase-table reconstruction, and fail-closed verification software.
\end{abstract}

\input{sections/introduction}
\input{sections/related_work}
\input{sections/mathematics}
\input{sections/computation}
\input{sections/neural_search}
\input{sections/verification}
\input{sections/evaluation}
\input{sections/reproducibility}
\input{sections/conclusion}

\appendix
\input{sections/appendices}

\begingroup
\small
\bibliographystyle{abbrv}
\bibliography{references}
\endgroup

\end{document}
